# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the data
I used the dataset `activity.zip` that was contained in Dr. Peng's Github repository. We can use the `unzip` function from the `utils` package to automate the unzipping of the file.
```{r}
library(utils)
unzip("activity.zip")
dat <- read.csv("activity.csv", na.strings = "NA")
```

We can see three variables in the dataset, `steps`, `date`, and `interval`.
```{r}
str(dat)
```

Date is a factor variable so we can change this to the `Date` class for more convenient calculations.

```{r}
dat$date <- as.Date(as.character(dat$date))
str(dat$date)
summary(dat)
```

## What is mean total number of steps taken per day?

Make a histogram of the total number of steps taken each day  

One way to calculate the sum of the number of steps taken each day is to use the `ddply` function from the `plyr` package. 
```{r}
library(plyr)
total_steps_by_day <- ddply(.data = dat, .variables = .(date), summarize, total_steps = sum(steps, na.rm = T))
head(total_steps_by_day)
```

We can plot this using the base graphics system.

```{r}
hist(total_steps_by_day$total_steps, main = "Distribution of Total Steps by Day", xlab = "Total Steps")
```

Calculate and report the mean and median of the total number of steps taken per day

```{r}
mean_median_steps_by_day <- ddply(.data = dat, .variables = .(date), summarize, mean_steps = mean(steps, na.rm = T), median_steps = median(steps, na.rm = T))
mean_median_steps_by_day
```

## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
